Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-04-05 manuscript.tex
move to Elsevier

\documentclass[lettersize,journal]{IEEEtran}
% code

\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{q}\kern-.125emX}}

% \usepackage{balance}
\def\pub{false} % true for publication, false for draft
\newcommand*{\template}{template}
\input{\template/preamble/preamble_conf.tex}

\newcommand*{\fe}{\mv{r}}

\begin{document}
\title{
Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
%Constrained Optimization-Based neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems With Input Constraints/
}

\markboth{IEEE TRANSACTIONS ON NEURAL NETWORKS AND LEARNING SYSTEMS,
~Vol.~00, No.~0, Month~2024
}%
{How to Use the IEEEtran \LaTeX \ Templates}

\maketitle

\begin{abstract}
    This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints. A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints. The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
\end{abstract}

\begin{IEEEkeywords}
Neuro-adaptive control, constrained optimization, deep neural network, Euler-Lagrange system, input constraint.
\end{IEEEkeywords}

@@

\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.

More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Farrell:2006aa}. 
NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations. 
SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2017aa}. 
Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.

@@

The remainder of this paper is organized as follows. 
Section \ref{sec:Problem Formulation} presents the target system and control objective.
Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
Candidates of input constraints are presented in Section \ref{sec:appen:cstr}.
Section \ref{sec:stability} analyzes the stability of the proposed controller.
A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
% The appendices provide the proof of the lemma used in the stability analysis.

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    (
        \Vert \estwth_i\Vert^2 
        -
        \bar\theta_i^2 
    )    
    \le 0
    \label{eq:cstr:weight_ball}
\end{equation}
with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight_ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.

@@

\begin{theorem}
    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$. 
    This holds with the weight norm constraint \eqref{eq:cstr:weight_ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
\end{theorem}

@@

%  SECTION SIMULATION ======================================
\section{Simulation}\label{sec:sim}

\subsection{Setup}

The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
%This model contains terms of gravity and friction in its mechanical system.
%These terms make system functions in \eqref{eq. system dynamics 1} nonlinear.
%and can be considered as the disturbance of the system.
The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for $\q=[q_1,q_2]^\top $ was defined as
\begin{equation}
    {q_d}(t) = 
    \begin{bmatrix}
        {q_d}_1\\{q_d}_2
    \end{bmatrix}
    =
    \begin{bmatrix}
        +\cos(0.5\pi t) + 1 \\
        -\cos(0.5\pi t) - 1 
    \end{bmatrix}.
\end{equation}
%\color{red}
%Considering the power limitation of the power source for the actuators [], 
The control input saturation function was defined as $h(\tau):= \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{Vasquez-Plaza:2023aa} and is given by
\begin{equation}
    \text{SSF}_L^U(\Vert\tau\Vert) = {\Vert\tau\Vert\over (1+(\Vert\tau\Vert/\bar\tau)^p)^{1/p}}.
    \label{eq. h func}
\end{equation}
with $p$ being the smoothing factor. The effect of $p$ and the boundedness of $\Vert\partial h/\partial \tau\Vert_F$ is shown in Fig.~\ref{fig: h func}.
The parameters of the control input saturation function were selected as $p=100$ and $\bar\tau=50$.

In addition to this physically imposed control input saturation, the input norm constraint \eqref{eq. cstr input ball} was imposed to ensure that the control input $\tau$ stays within the unsaturation region of $h(\tau)$ and to prevent inefficient use of the input. With a sufficiently large value for $p$, the input norm constraint essentially matches the control input saturation function. Note that among the selected controllers given below, only the proposed CoNAC can rigorously handle this input norm constraint.

% **********************************************************
% SYSTEM FIGURE AND TABLE
\begin{figure}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{fig/RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \centering
    \begin{tabular}{c m{11em} c c c }
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass of $p\textsuperscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_p$  & Length of $p\textsuperscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
    \hline
    ${l_c}_p$ & COM of $p\textsuperscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $b_p$   & Viscous coef. of $p\textsuperscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    ${f_c}_p$  & Friction coef. of $p\textsuperscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}

\begin{figure}[!t]
    \centering
    \includegraphics[width=0.9\linewidth]{fig/fig13.eps}
    \caption{Effect of parameter $p$ in the control input saturation function $h$ and boundedness of $\Vert\partial h/\partial \tau\Vert_F$.}
    \label{fig: h func}
\end{figure}

% SYSTEM FIGURE AND TABLE
% **********************************************************
Four controllers were examined for a comparative study. The first was the Backstepping Controller (BSC), used as the baseline. The second was the DNN-based Backstepping Controller (DNN-BSC), an existing neuro-adaptive control method where a DNN was employed to learn and compensate for the lumped system uncertainty function $f$ in the BSC. While this method addressed the weight norm constraint via a projection operator, it did not account for either the input norm or input bound constraints. The third was DNN-BSC augmented with an auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (DNN-BSC-A), which handled the (linear) input saturation constraint but not the nonlinear input norm constraint. As a result, an approximation of the input norm constraint was used as an input bound constraint. Lastly, the proposed controller, CoNAC, rigorously considered system uncertainties, the weight norm constraint, and input constraints within a constrained optimization framework. The properties of these four controllers are summarized in Table \ref{table:controller}.
%and control input ball constraints presented in Appendix \ref{sec:cstr candidates}, included (named CoNAC).

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{|c||c|c|c|}
    \hline
    & \multicolumn{3}{c|}{Handling Capability}\\
    \hline
    & System & Weight Norm & Input Norm\\
    &  Uncertainty & Constraint & Constraint\\
    \hline 
    BSC     & X & X & X\\
    \hline
    \multirow{2}{*}{DNN-BSC}     & \multirow{2}{*}{O} & O & \multirow{2}{*}{X}\\
         &  & (by projection) & \\
    \hline
    \multirow{2}{*}{DNN-BSC-A}   & \multirow{2}{*}{O} & O & $\triangle$ \\
       &  & (by projection) &  (by aux. system)\\
       % &  & & linearized constraint)\\
    % \hline
    % \multirow{3}{*}{DNN-BSC-A}   & \multirow{3}{*}{O} & O & $\triangle$ (by auxiliary\\
    %    &  & (by projection) &  system for \\
    %    &  & & linearized constraint)\\
    \hline
    \multirow{2}{*}{CoNAC}     &  \multirow{2}{*}{O} & O & O\\
         &  & (by optimization) & (by optimization)\\
    \hline
    \end{tabular}
\end{table}

% \begin{table}
% \caption{Specifications of the IPMSM Drive Used in the Experiment}\label{Tab3}
% \centering
% {\begin{tabular}{cc}\textcolor{black}ine
% \multicolumn{2}{c}{IPMSM}\\\textcolor{black}ine\textcolor{black}ine
% Rated power & 3 kW\\
% Rated speed & 4500 RPM\\
% Rated torque & 6.4 Nm\\
% Rotor inertia & 0.0021 kg$\cdot$m$^2$\\
% $I_{max}$ & 15 A \\
% $V_{dc}$ & 100 V\\
% $R_s$ & 0.34 $\Omega$\\
% $P$ & 3\\
% $T_s$ & 20 $\mu$s \\\textcolor{black}ine
% \multicolumn{2}{c}{Inverter}\\\textcolor{black}ine\textcolor{black}ine
% \multirow{2}{*}{Controller} & TMS320F28377D\\
% & (Texas Instrument) \\
% \multirow{2}{*}{IGBT module} & FS400R07A1E3\\
%  & (Infineon Technologies)
% \\\textcolor{black}ine
% \end{tabular}}
% \end{table}

% \begin{table}[!t]
%     \renewcommand{\arraystretch}{1.3}
%     \caption{Common Parameters of Selected Controllers.}
%     \label{table: error norm}
%     \centering
%     \begin{tabular}{|c||c|c|c|c|c|c|}
%     \hline
%     & $\alpha$ & ${k_q}$& ${k_z}$ & $M_0$ & $C_0$ & $G_0$ \\
%     \hline 
%     CM1 & - & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
%     \hline
%     CM2 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
%     \hline
%     CM3 & 1e3 & 2 & 10 & $I_2$ & $I_2$ & $0_{2\times1}$\\
%     \hline
%     C & 1e3 & 2 & 10 & $I_2$ & - & -\\
%     \hline
%     \end{tabular}
%     \label{table: control parameters}
% \end{table}

>>>>

%% 
%% Copyright 2007-2025 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.3 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

% \documentclass[preprint,12pt,authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
\documentclass[final,3p,times,authoryear]{elsarticle}
% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

% \usepackage{balance}
\def\pub{false} % true for publication, false for draft
\newcommand*{\template}{template}
\input{\template/preamble/preamble_Elsevier.tex}

\newcommand*{\fe}{\mv{r}}
\DeclareMathOperator{\mypoly}{Poly} % filtered error

\newcommand*{\figSize}{.99}

% %% The amssymb package provides various useful mathematical symbols
% \usepackage{amssymb}
% %% The amsmath package provides various useful equation environments.
% \usepackage{amsmath}
% %% The amsthm package provides extended theorem environments
% %% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Nuclear Physics B}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

\title{
  Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
} %% Article title

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author{
  Myeongseok Ryu, Donghwa Hong, and Kyunghwan Choi
} %% Author name

%% Author affiliation
\affiliation{organization={
  Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology (GIST)
},%Department and Organization
            addressline={123 Cheomdangwagi-ro, Buk-gu}, 
            city={Gwangju},
            postcode={61005}, 
            state={},
            country={Korea}}

%% Abstract
\begin{abstract}
  This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints. A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints. The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Research highlight 1
\item Research highlight 2
\end{highlights}

%% Keywords
\begin{keyword}
Neuro-adaptive control \sep constrained optimization \sep deep neural network \sep Euler-Lagrange system \sep input constraint

%% keywords here, in the form: keyword \sep keyword
%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% Add \usepackage{lineno} before \begin{document} and uncomment 
%% following line to enable line numbers
%% \linenumbers

%% main text
%%

@@

Many engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.

More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Farrell:2006aa}. 
NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations. 
SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2018aa}. 
Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.

@@

The remainder of this paper is organized as follows. 
Section \ref{sec:Problem Formulation} presents the target system and control objective.
Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
Candidates of input constraints are presented in \ref{sec:appen:cstr}.
Section \ref{sec:stability} analyzes the stability of the proposed controller.
A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
% The appendices provide the proof of the lemma used in the stability analysis.

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    (
        \Vert \estwth_i\Vert^2 
        -
        \bar\theta_i^2 
    )    
    \le 0
    \label{eq:cstr:weight:ball}
\end{equation}
with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight:ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight:ball:grad}, respectively.

@@

\begin{theorem}
    For the dynamical system in \eqref{eq:sys1}, the neuro-adaptive controller \eqref{eq:control:est} and weight adaptation laws \eqref{eq:adaptation law} ensure the boundedness of the filtered error $\fe$ and the weight estimate $\estwth$. 
    This holds with the weight norm constraint \eqref{eq:cstr:weight:ball} and input constraints satisfying Assumption \ref{assum:convex} and \ref{assum:LICQ}.
\end{theorem}

@@

%  SECTION SIMULATION ======================================
\section{Implementation and Validation}\label{sec:sim}

The proposed CoNAC was validated via numerical simulations and real-time experiments on a two-link manipulator.

\subsection{Numerical Simulation Validation}

% ------------------------------------
% Robot Model and Reference Trajectory
% ------------------------------------
The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
The system dynamics of the two-link manipulator is described by the following equations:
\MSRY{ADD MORE DETAIL; Following Eqn is just example}
\begin{equation}
    \begin{aligned}
        \mm M(\q) \ddtt{\q} + \mm V_m(\q,\dot\q) + \mm F(\q,\dot\q) + \mm G(\q) = \mv\tau,
        \\
        \mv\tau = \estNN(\q,\dot\q),
    \end{aligned}
    \label{eq:robot_dynamics}
\end{equation}
The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ \MSRY{more parameters} denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
The values of the system model parameters are provided in Table~\ref{table:system:params}. 
The desired trajectory for $\q=[q_1,q_2]^\top $ was defined with \MSRY{5th Poly functions} as
\begin{equation}
  {q_d}(t) = 
  \begin{bmatrix}
      {q_d}_1\\{q_d}_2
  \end{bmatrix}
  =
  \begin{cases}
    \mypoly(\q_0,\q_1,t_f,t)
      & \text{if } 0\le t < t_f \\
    \mypoly(\q_1,\q_2,t_f,t-t_f)
      & \text{if } t_f\le t < 2t_f \\
    \mypoly(\q_2,\q_3,t_f,t-2t_f)
      & \text{if } 2t_f\le t < 3t_f \\
    \mypoly(\q_3,\q_0,t_f,t-3t_f)
      & \text{if } 3t_f\le t < 4t_f \\
  \end{cases}
  ,
  \label{eq:desired trajectory}
\end{equation}
where \MSRY{CAN BE CHANGED}$\q_0=[0,0]^\top$, $\q_1=[\pi/2,\pi/2]^\top$, $\q_2=[\pi/2,0]^\top$, $\q_3=[0,\pi/2]^\top$, and $t_f=5$ s.
\MSRY{VIDEO IS PROVIDED; IF WE CAN PROVIDE}

% ------------------------------------
% Control Input Saturation
% ------------------------------------
To demonstrate the effectiveness of the proposed CoNAC to handle the combination of the nonlinear input constraints, the following control input saturations were imposed:
\begin{equation}
  \mysat(\mv\tau) 
  =
  ,
  \label{eq:control input saturation}
\end{equation}
where $\bar\tau=50, \bar\tau_1$ and $\bar\tau_2$ are the saturation limit values for the norm of the control input and the first and second links, respectively.

% ------------------------------------
% Robot Model Figure and Table
% ------------------------------------
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\linewidth]{fig/RobotModel.drawio.png}
    \caption{Two-link manipulator model.}
    \label{fig: manipulator}
\end{figure}

\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \centering
    \begin{tabular}{c m{11em} c c c }
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass of $p\textsuperscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_p$  & Length of $p\textsuperscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
    \hline
    ${l_c}_p$ & COM of $p\textsuperscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $b_p$   & Viscous coef. of $p\textsuperscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    ${f_c}_p$  & Friction coef. of $p\textsuperscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    ${f_s}_p$  & ?? $p\textsuperscript{th}$ link &   (Nm) &  (Nm) \\
    \hline
    \end{tabular}
    \label{table:system:params}
\end{table}

% ------------------------------------
% Controllers
% ------------------------------------
For a comparative study, NAC with the auxiliary system presented in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa} (NAC-AUX) was implemented, which only considered the input bound constraint introcuded in \ref{sec:appen:cstr:input:norm} and not the nonlinear input norm constraint \eqref{eq:cstr:input:norm}.
As a result, an approximation of the input norm constraint was used as an input bound constraint. 
Besides, the proposed controller, CoNAC, rigorously considered the weight norm constraint, and input bound and norm constraints within a constrained optimization framework. 
The properties of these four controllers are summarized in Table \ref{table:controller}.

% ------------------------------------
% NAC-AUX
% ------------------------------------
The control law for NAC-AUX was the same CoNAC, but with an auxiliary system to compensate for control input violations. 
Since the auxiliary system handled only the input bound constraint, not the more complex input norm constraint \eqref{eq:cstr:input:norm}, an approximated version of the input norm constraint was used as an input bound constraint \eqref{eq:cstr:input:bound} with ${\overline\tau_i} = -{\underline\tau_i} = (\bar\tau/\sqrt{2}+\bar\tau)/2$. 
The comparison between the original input norm constraint and its approximation is shown in Fig.~\MSRY{ADD FIGURE}.
The auxiliary system is defined as $\ddtt{\mv\zeta} = \mm{A}_\zeta \mv{\zeta} + \mm{B}_\zeta \Delta\mv{\tau},\ \mv{\zeta}\vert_{t=0} = 0$, where $\mv{\zeta}\in\R^n$ denotes the auxiliary state, $\mm{A}_\zeta=-[20,0;0;20],\mm{B}_\zeta=[10,0;0,10]$\MSRY{SEE HERE}, and $\Delta\tau_{(i)} = 
\tau_{(i)}-\mysat(\tau_{(i)},{\overline\tau_i},{\underline\tau_i})$
The auxiliary state variables were used in the adaptation law \eqref{eq:adap:th:approx} by substituting $\fe$ with $\fe+\mv{\zeta}$.

% ------------------------------------
% CoNAC
% ------------------------------------
The proposed CoNAC directly approximated the control law using the DNN as defined in \eqref{eq:control:est}. 
The update rates for the multipliers were set as \MSRY{SEE HERE}$\beta_{j}=0.1$. The weight matrix $W$ was selected as $W=\text{diag}([5,1,15,15])]$.

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all DNN-based controllers (DNN-BSC, DNN-BSC-A, and CoNAC), the DNN input vector $q_{NN}$ was set as the desired trajectory for ${q}$, \ie $q_{NN}=[{q_d}^\top,1]^\top$ with the augmented scalar 1 included to account for the bias term in the weight matrix. 
Each DNN architecture had two hidden layers with eight nodes (\ie $k=2, l_0=2, l_1=8, l_2=8, l_3=2$), and the adaptation gain was set to $\alpha =10^3$. The constraint parameters were $\bar\wth_0=20, \bar\wth_1=30, \bar\wth_2=40$, and $\bar\tau = 50$ \MSRY{SEE HERE}. The control parameters for all the controllers were set as ${k_q}=1.1,{k_z}=10,M_0=I_2,C_0=I_2,G_0=[0,0]^\top$.
The sampling time of the simulations was selected as $T_s=10^{-4}$.
% The same values were assigned across all the controllers for the common parameters for a fair comparison.
The parameters for CoNAC to NAC-AUX were listed in Table.~\ref{table:controller:params}. 
% The same values were assigned across all the controllers for the common parameters for a fair comparison.

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Properties of the controllers used in simulation}
  \label{table:controller}
  \centering
  \begin{tabular}{c c c}
  \hline
  & \multicolumn{2}{c}{\bf{Handling Capability}}\\
  \hline
  \hline
  & Weight Norm Constraint & Input Norm Constraint\\
  \hline
  \hline
  \multirow{2}{*}{\bf{CoNAC}} & O & $\triangle$ \\
     & (by projection) &  (by aux. system)\\
  \hline
  \multirow{2}{*}{\bf{NAC-AUX}} & O & O\\
     & (by optimization) & (by optimization)\\
  \hline
  \end{tabular}
\end{table}

% ------------------------------------
% Controller Parameters
% ------------------------------------
\begin{table}[t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Parameters of the controllers used in simulation}
  \label{table:controller:params}
  \centering
  \begin{tabular}{c | c c c c c c c c c c c c c c}
  \hline
  & $l_0$ & $l_1$ & $l_2$ & $l_3$ & $\alpha$ & $\beta$ & $\bar\theta_0$ & $\bar\theta_1$ & $\bar\theta_2$ & $\bar\tau$ & $\tau_1$ & $\tau_2$ & $\mm{A}_\zeta$ & $\mm{B}_\zeta$ \\
  \hline
  \hline
    \bf{BSC} & \multirow{2}{*}{6} & \multirow{2}{*}{4} & \multirow{2}{*}{4} & \multirow{2}{*}{2} & \multirow{2}{*}{$10^3$} & \multirow{2}{*}{$10^{-4}$} & \multirow{2}{*}{11} & \multirow{2}{*}{12} & \multirow{2}{*}{13} & \multirow{2}{*}{10} & \multirow{2}{*}{11} & 0.5 & & \\
  % \hline
    \bf{NAC-AUX} &  & & & & & & & & & & & 0.5 & $[20,0;0,20]$ & $[10,0;0,10]$ \\
  \hline
  \end{tabular}
\end{table}

\begin{figure}[t]
  \centering
    \subfloat[Tracking result of $d$-axis stator current .]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/mearsurement/figures/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \vspace{2mm}
    \subfloat[Tracking result of $d$-axis stator current .]{
      \includegraphics[width=\figSize\linewidth]
      {
        src/mearsurement/figures/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vspace{2mm}
      \subfloat[Control input.]{
        \includegraphics[width=\figSize\linewidth]
        {
          src/mearsurement/figures/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \vspace{2mm}
      \subfloat[Control input.]{
        \includegraphics[width=\figSize\linewidth]
        {
          src/mearsurement/figures/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
  \caption{
  Simulation results of the CoNAC (blue) and NAC-AUX (cyan), and reference signal of ${\q}_d$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure}
